---
title: "angelo2"
author: "StephanLewandowsky"
date: "2019-10-25"
output: 
   workflowr::wflow_html:
     code_folding: hide
     number_sections: yes
     toc: yes
     toc_depth: 3
     toc_float: yes
     theme: cosmo
     highlight: textmate
editor_options:
  chunk_output_type: console
---

## Setup and read data
```{r echo=TRUE, warning=FALSE, message=FALSE, results="hide"}
rm(list=ls())
library(lattice)
library(hexbin) #helps with large data sets in lattic scatterplot matrix
library(stargazer)
library(tidyverse)
library(lme4)
library(lavaan)
library(semPlot)
library(semTools)
library(RColorBrewer)
library(gridExtra)
library(stringr)
library(Hmisc)
library(reshape2)
library(psych)
library(scales)
library(summarytools) #contains descr()
library(workflowr)

source("analysis/funcs.r")

revscore <- function (x,cluster) {  #this reverse scores a scale for items of reversed polarity
  return ((likert[cluster]+1)-x)            
}

#define working directories
inputdir <- "data"

## Reading data and variable names 
# csv created from "Study 2 - Data Matrix (with control item).xlsx" on 11/11/19.
angelo2raw <- read.csv(paste(inputdir,"Study 2 - Data Matrix.csv",sep="/"),header=TRUE,row.names=NULL) 
```

## Cleaning data
```{r clean, echo=TRUE, warning=FALSE, message=FALSE, results="hide"}
names(angelo2raw)[1] <- "Control"
angelo2 <- angelo2raw %>% filter(Control==1) %>% select(-Control)

```


## Correlations before reverse scoring and then reverse score
```{r reverse, echo=TRUE, warning=FALSE, message=FALSE, results="hide"}
itemclusters  <- c("PSEUDO", "PITS.PSEUDO", "IAS.PSEUDO", "GIS.PSEUDO", "SDQ.PSEUDO")
likert        <- c(5,5,4,6,7) #likert scales (for reverse scoring)
names(likert) <- itemclusters

# pre-reverse correlations
sapply(itemclusters,FUN=function(cluster) {
  angelo2 %>% select(starts_with(cluster)) %>% cor %>% print
})

# all variables to be reverse-scored contain ".R" in name
angelo2r <- select(angelo2,Age:starts_with("Political")) #grab first bit, then add columns
sapply(itemclusters,FUN=function(cluster) {
  angelo2r <<- cbind(angelo2r, angelo2 %>% select(starts_with(cluster)) %>% mutate_at(vars(contains(".R")),revscore,cluster)) 
})
```


## Basic summaries
```{r summaries, echo=TRUE}
descr(angelo2r)
```

## Correlations after reverse scoring
```{r corrs2, echo=TRUE}
sapply(itemclusters,FUN=function(cluster) {
  angelo2r %>% select(starts_with(cluster)) %>% cor 
})
```


## Correlations among composites retaining all items
```{r composites, echo=TRUE}

angelocomps <- NULL
for (cluster in itemclusters) {
  angelocomps <- cbind(angelocomps, angelo2r %>% select(starts_with(cluster)) %>% apply(.,1,mean,na.rm=TRUE))
}
angelocomps <- as.data.frame(angelocomps)
names(angelocomps) <- itemclusters
angelocomps <- cbind(select(angelo2r,Age:starts_with("Political")), angelocomps)

cor(angelocomps %>% select(-c(Age:starts_with("Political"))))

```  

## Look at reliabilities
```{r alpha, echo=TRUE}
# e.g. http://www.statsoft.com/Textbook/Reliability-and-Item-Analysis#classical
#first print
sapply(itemclusters,FUN=function(cluster) {
  angelo2r %>% select(starts_with(cluster)) %>% psych::alpha(.) %>% print
})
#now retain output for further processing
a2alphas <- sapply(itemclusters,FUN=function(cluster) {
  angelo2r %>% select(starts_with(cluster)) %>% psych::alpha(.) 
})

#drop items based on cutoffs e.g. https://rpubs.com/hauselin/reliabilityanalysis 
r.drop.cutoff   <- .3
max.resp.cutoff <- .8

tbditems<- NULL
for (cluster in itemclusters) {
  thisscale <-  a2alphas[,cluster]
  tbditems <- c(tbditems,
                unique(c(rownames(thisscale$item.stats)[thisscale$item.stats$r.drop < r.drop.cutoff],
                         rownames(thisscale$response.freq) [apply(thisscale$response.freq,1,max) > max.resp.cutoff])))
}
angelo2rfin <- angelo2r %>% select(-tbditems)
```

## Redo reliability analysis after eliminating items 
```{r alpha2, echo=TRUE}
sapply(itemclusters,FUN=function(cluster) {
  angelo2rfin %>% select(starts_with(cluster)) %>% psych::alpha(.) %>% print
})
```

## Distribution of composites after elimination of items
```{r compositesplot, echo=TRUE}

angelocomps <- NULL
for (cluster in itemclusters) {
  angelocomps <- cbind(angelocomps, angelo2rfin %>% select(starts_with(cluster)) %>% apply(.,1,mean,na.rm=TRUE))
}
angelocomps <- as.data.frame(angelocomps)
names(angelocomps) <- itemclusters
angelocomps <- cbind(select(angelo2rfin,Age:starts_with("Political")), angelocomps)

hist(angelocomps %>% select(-c(Age:starts_with("Political"))))

#focus on PITS.PSEUDO
table(angelo2rfin %>% select(starts_with("PITS")) %>% apply(.,1,sum))

#tbk <- angelo2rfin %>% select(starts_with("PITS")) %>% apply(.,1,sum)!=50

```

## Correlations among composites after elimination of items
```{r compositescor, echo=TRUE}

cor(angelocomps %>% select(-c(Age:starts_with("Political"))))

```  

## Check for nonlinearities in pairwise composite correlations
```{r nonlinplots, echo=TRUE}
splom(angelocomps %>% select(-c(Age:starts_with("Political"))),
      panel=panel.hexbinplot,
      lower.panel = function(x, y, ...){
            panel.hexbinplot(x, y, ...)
            panel.loess(x, y, ..., col = 'red',lwd=2)
      })
```  

